DataCleaning

### 2014-08-05 DataManipulation/DataManipulation.Rmd
Updated data with July and reran.  I could probably use another month of data.

#Get the names of the trend files
TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")

#all the trends in one data frame
AllTrends<-as.data.frame(lapply(TrendsFiles,FUN=ReadTrends))

@@

Loads<- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-hourly-loads.csv")

Forecasts <- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-rto-forecasts.csv")
```

@@

#Make sure we only have day ahead forecasts
table(Forecasts$Forecasted-Forecasts$ForecastDate)
Forecasts<-Forecasts[Forecasts$Forecasted-Forecasts$ForecastDate<0,]

>>>>

#Get the names of the trend files
TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")
#Removing the subdirectory
TrendsFiles[-12]

#all the trends in one data frame
AllTrends<-as.data.frame(lapply(TrendsFiles[-12],FUN=ReadTrends))

@@

Loads<- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-hourly-loads.csv",header = TRUE)

Forecasts <- read.csv("~/Research/Forecast-Peak-With-Google-Trends/LoadAndForecastData/2014-rto-forecasts.csv",header = TRUE)
```

@@

#Make sure we only have day ahead forecasts
table(Forecasts$Forecasted-Forecasts$ForecastDate)
Forecasts<-Forecasts[Forecasts$Forecasted-Forecasts$ForecastDate<(-82800) ,]
